
\thispagestyle{empty}
\setstretch{1.4}
    
\begin{center}
   \vspace{1cm}
    \large{Department of Physics\\Institute for Theoretical Physics\\ University of Tübingen, Germany\\
   Master Degree in Astro \& Particle Physics\\
   %Academic Year 2024-2025\\
   \today}\\
    \vspace{1.5cm} 
    Master's Thesis 

    \rule{\textwidth}{1pt}
    \begin{minipage}{\textwidth}
        \centering
        
        \vspace{0.8cm}
        \textbf{\huge{Transverse Spin Effects\\ at NLO Accuracy in Semi-Inclusive Deep Inelastic Scattering}}
        \vspace{0.8cm}
        
    \end{minipage}
    \rule{\textwidth}{1pt}
\end{center}

\vspace{20mm}

\noindent
\begin{minipage}[t]{0.45\textwidth} \raggedright 
{\Large Supervisor:\\ {\bf Prof. Marc Schlegel}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth} \raggedleft
{\Large  Student: \\ {\bf Diego Scantamburlo}}
\end{minipage}
\vspace{5mm}

\noindent
\begin{minipage}[t]{0.55\textwidth}\raggedright 
{\Large Co-supervisor:\\ {\bf Prof. Werner Vogelsang}}
\end{minipage}

\vfill


\newpage
\newpage
\pagenumbering{Roman}

\vspace{6cm}
\textit{Let's twist again!}
\newpage
\textit{Blank}
\newpage
\section*{Statement of originality}
Hereby I confirm, Diego Scantamburlo, Matr. Nr. XYZ, that this assignment is my own work and that I have only sought and used mentioned tools. I have clearly referenced in the text and the bibliography all sources used in the work (printed sources, internet or any other source), including verbatim citations or paraphrases. I am aware of the fact that plagiarism is an attempt to deceit which, in case of recurrence, can result in a loss of test authorization. Furthermore, I confirm that neither this work nor parts of it have been previously, or concurrently, used as an exam work - neither for other courses nor within other exam processes.

Place and date Signature XYZ

\newpage
\textit{Blank}
\newpage
\section*{Acknowledgements}
\newpage
\textit{Blank}

\tableofcontents


